\chapter{Understanding Windows Azure}
\section{What's Windows Azure?}
"Azure can be anything you want it to be" as described by Microsoft.\\
Platform from Microsoft that provides a wide range of different services,Simply it's collection of integrated cloud services that developers and IT professionals use to build, deploy, and manage applications through our global network of data-centers.

\subsection{Why cloud?}
Noways, businesses use cloud computing as cloud can provide users with a number of different benefits.
\\
Cost: Reduction of cost.
\\
Flexibility: Cloud computing allows users suit their needs and to switch applications easily and rapidly. 
\\
Universal access: allow remotely employees access for work via Internet.
\\
Pay as you go: Choosing the best option for user's needs. Cloud computing also allows a business to use, access and pay only for what they use, with a fast implementation time


\subsection{Windows Azure services}
Windows Azure provides businesses with four basic categories of cloud-based services:\\
Compute services\\
Network services\\
Data services\\
App services\\
Compute services:\\
Virtual Machines:\\
lets user create, deploy, and manage virtual machines running in the Windows Azure cloud.\\
Web Sites:\\
Provides user with a managed web environment you can use
to create new websites or migrate your existing business website into the cloud.\\
Cloud Services.\\
allows users to build and deploy highly available and
almost infinitely scalable applications with low administration costs using almost any
programming language.
Mobile Services.\\
provides solution for building, deploying
applications and storing data for mobile devices.